### 2023-01-17 output/DiD/tables/pre_treatment_covariate_tests.tex
Added covariate tests table

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{r}{Dependent Variable} \\
 &  & Zestimate, Dec. 2022 & Plaintiff victory \\
\midrule
\multirow[c]{3}{3cm}{Panel A: Pre-treatment Zestimates} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
 & Zestimate, Jan. 2018 & 0.00 & 0.00 \\
 & Change from Jan. 2018 to Jan. 2019 & 0.00 & 0.27 \\
\multirow[c]{3}{3cm}{Panel B: Census Tract Characteristics} & Median household income (2016) & 0.00 & 0.01 \\
 & Population density (2010) & 0.00 & 0.01 \\
 & Portion white (2010) & 0.00 & 0.00 \\
\multirow[c]{3}{3cm}{Panel C: Case Initiation} & For cause & 0.01 & 0.68 \\
 & No cause & 0.98 & 0.03 \\
 & Non-payment of rent & 0.31 & 0.76 \\
\multirow[c]{4}{3cm}{Panel D: Defendant and Plaintiff Characteristics} & Defendant has an attorney & 0.37 & 0.00 \\
 & Plaintiff has an attorney & 0.61 & 0.48 \\
 & Defendant is an entity & 0.02 & 0.37 \\
 & Plaintiff is an entity & 0.63 & 0.12 \\
\multirow[c]{6}{3cm}{Panel E: Case Resolution} & Case duration & 0.57 & 0.00 \\
 & Case defaulted & 0.89 & 0.00 \\
 & Case dismised & 0.00 & 0.00 \\
 & Case heard & 0.25 & 0.00 \\
 & Money judgment & 0.88 & 0.00 \\
 & Case mediated & nan & nan \\
\multirow[c]{4}{3cm}{Panel F: Post-treatment Zestimates} & At filing date & 0.00 & 0.04 \\
 & One year after filing date & 0.00 & 0.05 \\
 & Two years after filing date & 0.00 & 0.01 \\
 & Three years after filing date & 0.00 & 0.08 \\
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
 &  & Zestimate, Dec. 2022 & Plaintiff victory \\
\midrule
\multirow[c]{3}{3cm}{\textit{Panel A: Pre-treatment Zestimates}} & Zestimate, Jan. 2017 & 0.00 & 0.00 \\
 & Zestimate, Jan. 2018 & 0.00 & 0.00 \\
 & Change from Jan. 2018 to Jan. 2019 & 0.00 & 0.27 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Median household income (2016) & 0.00 & 0.01 \\
 & Population density (2010) & 0.00 & 0.01 \\
 & Portion white (2010) & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & For cause & 0.01 & 0.68 \\
 & No cause & 0.98 & 0.03 \\
 & Non-payment of rent & 0.31 & 0.76 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.37 & 0.00 \\
 & Plaintiff has an attorney & 0.61 & 0.48 \\
 & Defendant is an entity & 0.02 & 0.37 \\
 & Plaintiff is an entity & 0.63 & 0.12 \\
\cline{1-4}
\multirow[c]{6}{3cm}{\textit{Panel E: Case Resolution}} & Case duration & 0.57 & 0.00 \\
 & Case defaulted & 0.89 & 0.00 \\
 & Case dismised & 0.00 & 0.00 \\
 & Case heard & 0.25 & 0.00 \\
 & Money judgment & 0.88 & 0.00 \\
 & Case mediated & nan & nan \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel F: Post-treatment Zestimates}} & At filing date & 0.00 & 0.04 \\
 & One year after filing date & 0.00 & 0.05 \\
 & Two years after filing date & 0.00 & 0.01 \\
 & Three years after filing date & 0.00 & 0.08 \\
\cline{1-4}
\bottomrule
\end{tabular}
